Experiment 1

### 2021-06-30 experiments/experiment 2/experiment 2.Rmd
update to experiment framework

```{r}
num_CB_strains <- 9
num_SB_strains <- 9
num_PB_strains <- 9
CB_var_range <- 0.015789474
CB_var_TO <- -5
SB_var_range <- 0.0015789474
SB_var_TO <- -20.5
PB_var_range <- 0.0015789474
PB_var_TO <- -20.5

@@

```{r}
default_9strain <- new_starter(n_CB = num_CB_strains,
                             n_SB = num_SB_strains,
                             n_PB = num_PB_strains,
                             values_initial_state = initial_pars_from)
CB_var_gmax_s <- seq(zero, unity, length=num_div_treatment_levels) * CB_var_range
CB_var_h_s = seq(zero, CB_var_TO, length=num_div_treatment_levels) * CB_var_range
SB_var_gmax_s <- seq(zero, unity, length=num_div_treatment_levels) * SB_var_range
SB_var_h_s = seq(zero, SB_var_TO, length=num_div_treatment_levels) * SB_var_range
PB_var_gmax_s <- seq(zero, unity, length=num_div_treatment_levels) * PB_var_range
PB_var_h_s = seq(zero, PB_var_TO, length=num_div_treatment_levels) * PB_var_range
var_expt <- tibble(CB_var_gmax_s,
                   CB_var_h_s,
                   SB_var_gmax_s,
                   SB_var_h_s,
                   PB_var_gmax_s,
                   PB_var_h_s)
var_expt <- var_expt %>%
  nest_by(CB_var_gmax_s, CB_var_h_s,
          SB_var_gmax_s, SB_var_h_s,
          PB_var_gmax_s, PB_var_h_s) %>%
  mutate(pars = list(add_strain_var(default_9strain,
                                    CB_var_gmax = CB_var_gmax_s,
                                    CB_var_h = CB_var_h_s,
                                    SB_var_gmax = SB_var_gmax_s,
                                    SB_var_h = SB_var_h_s,
                                    PB_var_gmax = PB_var_gmax_s,
                                    PB_var_h = PB_var_h_s)))
```

@@

```{r}
sim_number1 <- 1
default_log10a_series <- c(-1, -8, -1)
initial_state <- new_initial_state(num_CB_strains,
                                   num_PB_strains,
                                   num_SB_strains,
                                   values = "bush_ssfig3")
initial_state[grep("CB_", names(initial_state))] <- 10/num_CB_strains
sim_res_novar <- run_simulation(parameter_values = var_expt$pars[[sim_number1]],
                          initial_state = initial_state)
plot_dynamics(sim_res_novar)
##ggsave(here("simulations/expt2/figures/switching_novar.pdf"), width = 10)
```

@@

```{r}
sim_number2 <- 2
sim_res_highvar <- run_simulation(parameter_values = var_expt$pars[[sim_number2]],
                          initial_state = initial_state)
plot_dynamics(sim_res_highvar)
##ggsave(here("expteriment 2/figures/switching_highvar.pdf"), width = 10)

@@

soi <- "O"
ggplot() +
  geom_path(data = filter(tmp_novar,functional_group == soi),
            aes(x=a, y = log10(Total_quantity), group = direction)) +
  geom_path(data = filter(tmp_highvar,functional_group == soi),
            aes(x=a, y = log10(Total_quantity), group = direction),
            linetype = "dashed", lwd=2, col="red") +
  ggtitle("Solid line is with no intraspecific diversity.\nDashed line is with intraspecific diversity")
##ggsave(here("experiment 2/figures/switching_comparison.pdf"), width = 8, height = 10)

@@

```{r}
var_expt <- run_ss_var_experiment()
saveRDS(var_expt, here("experiments/experiment 2/data/ss_data.RDS"))
```

```{r}
result_index1 <- 1
p1  <- plot_ss_result1(var_expt,
                result_index = result_index1,
                filename_prefix = NULL,
                save_image_file = FALSE)
p1
```

>>>>

```{r}
num_CB_strains <- 9
num_SB_strains <- 9
num_PB_strains <- 9
CB_gmax_div <- 0.015789474
CB_h_div <- -0.08
SB_gmax_div <- 0.015789474 * 0.5
SB_h_div <- -0.323 * 0.5
PB_gmax_div <- 0.015789474 * 0.5
PB_h_div <- -0.323 * 0.5

@@

```{r}
default_9strain <- new_starter(n_CB = num_CB_strains,
                             n_SB = num_SB_strains,
                             n_PB = num_PB_strains,
                             values_initial_state = initial_pars_from)
CB_var_gmax_s <- seq(zero, unity, length=num_div_treatment_levels) * CB_gmax_div
CB_var_h_s = seq(zero, unity, length=num_div_treatment_levels) * CB_h_div
SB_var_gmax_s <- seq(zero, unity, length=num_div_treatment_levels) * SB_gmax_div
SB_var_h_s = seq(zero, unity, length=num_div_treatment_levels) * SB_h_div
PB_var_gmax_s <- seq(zero, unity, length=num_div_treatment_levels) * PB_gmax_div
PB_var_h_s = seq(zero, unity, length=num_div_treatment_levels) * PB_h_div
var_expt <- tibble(CB_var_gmax_s,
                   CB_var_h_s,
                   SB_var_gmax_s,
                   SB_var_h_s,
                   PB_var_gmax_s,
                   PB_var_h_s)
var_expt <- var_expt %>%
  nest_by(CB_var_gmax_s, CB_var_h_s,
          SB_var_gmax_s, SB_var_h_s,
          PB_var_gmax_s, PB_var_h_s) %>%
  mutate(pars = list(add_strain_var(default_9strain,
                                    CB_var_gmax = CB_var_gmax_s,
                                    CB_var_h = CB_var_h_s,
                                    SB_var_gmax = SB_var_gmax_s,
                                    SB_var_h = SB_var_h_s,
                                    PB_var_gmax = PB_var_gmax_s,
                                    PB_var_h = PB_var_h_s)))
```

@@

```{r}
sim_number1 <- 1
default_log10a_series <- c(-1, -8, -1)
initial_state <- new_initial_state(num_CB_strains,
                                   num_PB_strains,
                                   num_SB_strains,
                                   values = "bush_ssfig3")
initial_state[grep("CB_", names(initial_state))] <- 10/num_CB_strains
sim_res_novar <- run_simulation(parameter_values = var_expt$pars[[sim_number1]],
                          initial_state = initial_state)
plot_dynamics(sim_res_novar)
#ggsave(here("simulations/expt2/figures/switching_novar.pdf"), width = 10)
```

@@

```{r}
sim_number2 <- 2
sim_res_highvar <- run_simulation(parameter_values = var_expt$pars[[sim_number2]],
                          initial_state = initial_state)
plot_dynamics(sim_res_highvar)
#ggsave(here("simulationsexpt2/figures/switching_highvar.pdf"), width = 10)

@@

soi <- "O"
ggplot() +
  geom_path(data = filter(tmp_novar,functional_group == soi),
            aes(x=a, y = log10(Total_quantity), group = direction)) +
  geom_path(data = filter(tmp_highvar,functional_group == soi),
            aes(x=a, y = log10(Total_quantity), group = direction),
            linetype = "dashed", lwd=2, col="red") +
  ggtitle("Solid line is with no intraspecific diversity.\nDashed line is with intraspecific diversity")
##ggsave(here("simulations/figures/switching_comparison.pdf"), width = 5, height = 4)

@@

```{r}
var_expt <- run_ss_var_experiment()
saveRDS(var_expt, here("experiments/experiment 2/data/ss_data.RDS"))

result_index1 <- 1
p1  <- plot_ss_result1(var_expt,
                result_index = result_index1,
                filename_prefix = NULL,
                save_image_file = FALSE)
p1
```

### 2021-06-30 experiments/tradeoff strength illustration.Rmd
update to experiment framework

```{r}
num_CB_strains <- 9
num_SB_strains <- 9
num_PB_strains <- 9
CB_var_range <- 0.015789474
CB_var_TO <- -20
SB_var_range <- 0.1
SB_var_TO <- -20
PB_var_range <- 0.1
PB_var_TO <- -20

@@

```{r}
default_9strain <- new_starter(n_CB = num_CB_strains,
                             n_SB = num_SB_strains,
                             n_PB = num_PB_strains,
                             values_initial_state = initial_pars_from)
CB_var_gmax_s <- seq(zero, unity*CB_var_TO, length=num_div_treatment_levels) * CB_var_range
CB_var_h_s = seq(zero, unity, length=num_div_treatment_levels) * CB_var_range
SB_var_gmax_s <- seq(zero, unity, length=num_div_treatment_levels) * SB_var_range
SB_var_h_s = seq(zero, SB_var_TO, length=num_div_treatment_levels) * SB_var_range
PB_var_gmax_s <- seq(zero, unity, length=num_div_treatment_levels) * PB_var_range
PB_var_h_s = seq(zero, PB_var_TO, length=num_div_treatment_levels) * PB_var_range
var_expt <- tibble(CB_var_gmax_s,
                   CB_var_h_s,
                   SB_var_gmax_s,
                   SB_var_h_s,
                   PB_var_gmax_s,
                   PB_var_h_s)
var_expt <- var_expt %>%
  nest_by(CB_var_gmax_s, CB_var_h_s,
          SB_var_gmax_s, SB_var_h_s,
          PB_var_gmax_s, PB_var_h_s) %>%
  mutate(pars = list(add_strain_var(default_9strain,
                                    CB_var_gmax = CB_var_gmax_s,
                                    CB_var_h = CB_var_h_s,
                                    SB_var_gmax = SB_var_gmax_s,
                                    SB_var_h = SB_var_h_s,
                                    PB_var_gmax = PB_var_gmax_s,
                                    PB_var_h = PB_var_h_s)))
```

@@

CBtraits <- tibble(var_expt$pars[[10]]$CB,
                     Diversity = "None",
                   Strength = "Strong")
CBtraits <- bind_rows(CBtraits,
                      tibble(var_expt$pars[[6]]$CB,
                     Diversity = "Medium",
                     Strength = "Strong"))
CBtraits <- bind_rows(CBtraits,
                      tibble(var_expt$pars[[1]]$CB,
                     Diversity = "High",
                     Strength = "Strong"))

````

@@

```{r}
num_CB_strains <- 9
num_SB_strains <- 9
num_PB_strains <- 9
CB_var_range <- 0.015789474
CB_var_TO <- -2
SB_var_range <- 0.1
SB_var_TO <- -20
PB_var_range <- 0.1
PB_var_TO <- -20

@@

```{r}
default_9strain <- new_starter(n_CB = num_CB_strains,
                             n_SB = num_SB_strains,
                             n_PB = num_PB_strains,
                             values_initial_state = initial_pars_from)
CB_var_gmax_s <- seq(zero, unity*CB_var_TO, length=num_div_treatment_levels) * CB_var_range
CB_var_h_s = seq(zero, unity, length=num_div_treatment_levels) * CB_var_range
SB_var_gmax_s <- seq(zero, unity, length=num_div_treatment_levels) * SB_var_range
SB_var_h_s = seq(zero, SB_var_TO, length=num_div_treatment_levels) * SB_var_range
PB_var_gmax_s <- seq(zero, unity, length=num_div_treatment_levels) * PB_var_range
PB_var_h_s = seq(zero, PB_var_TO, length=num_div_treatment_levels) * PB_var_range
var_expt <- tibble(CB_var_gmax_s,
                   CB_var_h_s,
                   SB_var_gmax_s,
                   SB_var_h_s,
                   PB_var_gmax_s,
                   PB_var_h_s)
var_expt <- var_expt %>%
  nest_by(CB_var_gmax_s, CB_var_h_s,
          SB_var_gmax_s, SB_var_h_s,
          PB_var_gmax_s, PB_var_h_s) %>%
  mutate(pars = list(add_strain_var(default_9strain,
                                    CB_var_gmax = CB_var_gmax_s,
                                    CB_var_h = CB_var_h_s,
                                    SB_var_gmax = SB_var_gmax_s,
                                    SB_var_h = SB_var_h_s,
                                    PB_var_gmax = PB_var_gmax_s,
                                    PB_var_h = PB_var_h_s)))
```

```{r}
CBtraits <- bind_rows(CBtraits,
                      tibble(var_expt$pars[[10]]$CB,
                     Diversity = "None",
                     Strength = "Weak"))
CBtraits <- bind_rows(CBtraits,
                      tibble(var_expt$pars[[6]]$CB,
                     Diversity = "Medium",
                     Strength = "Weak"))
CBtraits <- bind_rows(CBtraits,
                      tibble(var_expt$pars[[1]]$CB,
                     Diversity = "High",
                     Strength = "Weak"))

ggplot(CBtraits) +
  geom_point(aes(x = h_SR_CB, y = g_max_CB)) +
  facet_grid(Strength ~ Diversity) +
  xlab("Tolerance trait") +
  ylab("Maximum growth rate")

>>>>

```{r}
num_CB_strains <- 9
num_SB_strains <- 9
num_PB_strains <- 9
CB_gmax_div <- 0.015789474
CB_h_div <- -0.08
SB_gmax_div <- 0.015789474
SB_h_div <- -0.323
PB_gmax_div <- 0.015789474
PB_h_div <- -0.323

CB_var_range <- 0.015789474
CB_var_TO <- -20
SB_var_range <- 0.1
SB_var_TO <- -20
PB_var_range <- 0.1
PB_var_TO <- -20

@@

```{r}
default_9strain <- new_starter(n_CB = num_CB_strains,
                             n_SB = num_SB_strains,
                             n_PB = num_PB_strains,
                             values_initial_state = initial_pars_from)
CB_var_gmax_s <- seq(zero, unity, length=num_div_treatment_levels) * CB_gmax_div
CB_var_h_s = seq(zero, unity, length=num_div_treatment_levels) * CB_h_div
SB_var_gmax_s <- 1#seq(zero, unity, length=num_div_treatment_levels) * SB_gmax_div
SB_var_h_s = 1#seq(zero, unity, length=num_div_treatment_levels) * SB_h_div
PB_var_gmax_s <- 1#seq(zero, unity, length=num_div_treatment_levels) * PB_gmax_div
PB_var_h_s = 1#seq(zero, unity, length=num_div_treatment_levels) * PB_h_div
var_expt <- crossing(CB_var_gmax_s,
                   CB_var_h_s,
                   SB_var_gmax_s,
                   SB_var_h_s,
                   PB_var_gmax_s,
                   PB_var_h_s)
var_expt <- var_expt %>%
  nest_by(CB_var_gmax_s, CB_var_h_s,
          SB_var_gmax_s, SB_var_h_s,
          PB_var_gmax_s, PB_var_h_s) %>%
  mutate(pars = list(add_strain_var(default_9strain,
                                    CB_var_gmax = CB_var_gmax_s,
                                    CB_var_h = CB_var_h_s,
                                    SB_var_gmax = SB_var_gmax_s,
                                    SB_var_h = SB_var_h_s,
                                    PB_var_gmax = PB_var_gmax_s,
                                    PB_var_h = PB_var_h_s)))
```

@@

med_gmax <- 0.007017544
med_h <- -0.035555556
high_gmax <- 0.015789474
high_h <- -0.080

CBtraits <- tibble(var_expt$pars[[which(var_expt$CB_var_gmax_s == 0 &
                                          var_expt$CB_var_h_s == 0)]]$CB,
                     Div_gmax = "None",
                   Div_h = "None")
CBtraits <- bind_rows(CBtraits,
                      tibble(var_expt$pars[[which(var_expt$CB_var_gmax_s == 0 & abs(var_expt$CB_var_h_s - med_h)<0.0001)]]$CB,
                     Div_gmax = "None",
                   Div_h = "Medium"))
CBtraits <- bind_rows(CBtraits,
                      tibble(var_expt$pars[[which(var_expt$CB_var_gmax_s == 0 & abs(var_expt$CB_var_h_s - high_h)<0.0001)]]$CB,
                     Div_gmax = "None",
                   Div_h = "High"))

CBtraits <- bind_rows(CBtraits,
                      tibble(var_expt$pars[[which(abs(var_expt$CB_var_gmax_s - med_gmax)<0.0001 & abs(var_expt$CB_var_h_s - 0)<0.0001)]]$CB,
                     Div_gmax = "Medium",
                   Div_h = "None"))
CBtraits <- bind_rows(CBtraits,
                      tibble(var_expt$pars[[which(abs(var_expt$CB_var_gmax_s - med_gmax)<0.0001 & abs(var_expt$CB_var_h_s - med_h)<0.0001)]]$CB,
                     Div_gmax = "Medium",
                   Div_h = "Medium"))
CBtraits <- bind_rows(CBtraits,
                      tibble(var_expt$pars[[which(abs(var_expt$CB_var_gmax_s - med_gmax)<0.0001 & abs(var_expt$CB_var_h_s - high_h)<0.0001)]]$CB,
                     Div_gmax = "Medium",
                   Div_h = "High"))

CBtraits <- bind_rows(CBtraits,
                      tibble(var_expt$pars[[which(abs(var_expt$CB_var_gmax_s - high_gmax)<0.0001 & abs(var_expt$CB_var_h_s - 0)<0.0001)]]$CB,
                     Div_gmax = "High",
                   Div_h = "None"))
CBtraits <- bind_rows(CBtraits,
                      tibble(var_expt$pars[[which(abs(var_expt$CB_var_gmax_s - high_gmax)<0.0001 & abs(var_expt$CB_var_h_s - med_h)<0.0001)]]$CB,
                     Div_gmax = "High",
                   Div_h = "Medium"))
CBtraits <- bind_rows(CBtraits,
                      tibble(var_expt$pars[[which(abs(var_expt$CB_var_gmax_s - high_gmax)<0.0001 & abs(var_expt$CB_var_h_s - high_h)<0.0001)]]$CB,
                     Div_gmax = "High",
                   Div_h = "High"))

@@

```{r}
# num_CB_strains <- 9
# num_SB_strains <- 9
# num_PB_strains <- 9
# CB_var_range <- 0.015789474
# CB_var_TO <- -2
# SB_var_range <- 0.1
# SB_var_TO <- -20
# PB_var_range <- 0.1
# PB_var_TO <- -20
# 
# num_div_treatment_levels <- 10
```

@@

```{r}
# default_9strain <- new_starter(n_CB = num_CB_strains,
#                              n_SB = num_SB_strains,
#                              n_PB = num_PB_strains,
#                              values_initial_state = initial_pars_from)
# CB_var_gmax_s <- seq(zero, unity*CB_var_TO, length=num_div_treatment_levels) * CB_var_range
# CB_var_h_s = seq(zero, unity, length=num_div_treatment_levels) * CB_var_range
# SB_var_gmax_s <- seq(zero, unity, length=num_div_treatment_levels) * SB_var_range
# SB_var_h_s = seq(zero, SB_var_TO, length=num_div_treatment_levels) * SB_var_range
# PB_var_gmax_s <- seq(zero, unity, length=num_div_treatment_levels) * PB_var_range
# PB_var_h_s = seq(zero, PB_var_TO, length=num_div_treatment_levels) * PB_var_range
# var_expt <- tibble(CB_var_gmax_s,
#                    CB_var_h_s,
#                    SB_var_gmax_s,
#                    SB_var_h_s,
#                    PB_var_gmax_s,
#                    PB_var_h_s)
# var_expt <- var_expt %>%
#   nest_by(CB_var_gmax_s, CB_var_h_s,
#           SB_var_gmax_s, SB_var_h_s,
#           PB_var_gmax_s, PB_var_h_s) %>%
#   mutate(pars = list(add_strain_var(default_9strain,
#                                     CB_var_gmax = CB_var_gmax_s,
#                                     CB_var_h = CB_var_h_s,
#                                     SB_var_gmax = SB_var_gmax_s,
#                                     SB_var_h = SB_var_h_s,
#                                     PB_var_gmax = PB_var_gmax_s,
#                                     PB_var_h = PB_var_h_s)))
```

```{r}
# CBtraits <- bind_rows(CBtraits,
#                       tibble(var_expt$pars[[10]]$CB,
#                      Diversity = "None",
#                      Strength = "Weak"))
# CBtraits <- bind_rows(CBtraits,
#                       tibble(var_expt$pars[[6]]$CB,
#                      Diversity = "Medium",
#                      Strength = "Weak"))
# CBtraits <- bind_rows(CBtraits,
#                       tibble(var_expt$pars[[1]]$CB,
#                      Diversity = "High",
#                      Strength = "Weak"))

ggplot(CBtraits) +
  geom_point(aes(x = h_SR_CB, y = g_max_CB)) +
  facet_grid(Div_gmax ~ Div_h) +
  xlab("Tolerance trait") +
  ylab("Maximum growth rate")
